Automatic Parallelization and Transparent Fault Tolerance\\ (New project paper)

### 2016-04-05 pubs/tfp16/paper.tex
sync with Dean

\begin{abstract}
The claimed trend is an increasing appreciation and practice of functional
programming in scientific computing, and in particular strict (by default)
functional programming, in various guises.  Our project is the demonstration
of a light-weight, higher-order, polymorphic, pure functional language
implementation in which we can experiment with automatic parallelization
strategies and varying degrees of default strictness.  Non-strictness
constrains the degree of potential parallelism, that is, we are not exploring
speculative evaluation.  A secondary goal is to experiment with mechanisms
for transparent fault tolerance, another trend in scientific computing, and
by transitivity functional programming.
\\
\emph{Draft paper notes:}
\begin{enumerate}[before=\itshape]
  \item We are reporting work in progress.  At the time of writing we have a
    complete serial implementation, a primitive proof-of-concept parallel
    implementation, and are currently developing a more realistic parallel
    runtime.  We expect to have preliminary results from our new parallel
    implementation by the time of the symposium.  The fault-tolerance mechanisms
    remain future work.

@@

  \item Hopefully in the spirit of a student-friendly symposium, for this
    draft version we have chosen a more informal, conversational style of
    presentation than necessarily appropriate for a final paper, have
    highlighted student involvement and its influence on our approach, and
    included perhaps gratuitous detail about student contributions in particular.
  \end{enumerate}

>>>>

\begin{abstract}
A claimed trend is an increasing appreciation and practice of functional
programming in scientific computing, and in particular strict (by default)
functional programming, in various guises.  A second claimed trend in both
scientific computing and functional programming is transparent fault
tolerance.  Our project goal is the demonstration of a light-weight,
higher-order, polymorphic, pure functional language implementation in which we
can experiment with automatic parallelization strategies, varying degrees of
strictness, and mechanisms for transparent fault tolerance.
%We do not consider speculative evaluation, or semantic strictness inferred by
%program analysis, so potential parallelism is dictated by the degree of
%strictness.
\\
\emph{Draft paper notes:}
\begin{enumerate}[before=\itshape]
\item We are reporting work in progress.  At the time of writing we have a
  complete serial implementation, a primitive proof-of-concept parallel
  implementation, and are currently developing a more realistic parallel
  runtime.  We expect to have preliminary results from our new parallel
  implementation by the time of the symposium.  The fault-tolerance mechanisms
  remain future work.

@@

\item Hopefully in the spirit of a student-friendly symposium, for this draft
  version we have chosen a more informal, conversational style of presentation
  than necessarily appropriate for a final paper, have highlighted student
  involvement and its influence on our approach, and pointed out
  student contributions in particular.
\end{enumerate}
